\documentclass{article}
\usepackage[cm]{fullpage}
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\society}{Aberystwyth Live Action Games Society}

\newcommand{\by}[1]{\hfill {\em-- #1}}
\begin{document}
\small

% Title page
\title{\society{} General Meeting}
\date{29th May 2012}
\maketitle{}

\section{Apologies and Attendance}
	Seth Khan, Vice President, has stated that he will not be present at the meeting.

\section{Agenda}

	\begin{itemize}
		\item \textbf{Welcome from President} \\ Sam Clements, President, will talk on the subject of the society's future.
		\item \textbf{Constitution} \by{Sam Clements}
		\begin{itemize}
			\item The members present at the meeting will discuss the constitution and debate on what should be kept and new items can be added. This new constitution will be finalized and handed into the guild.
			\item Consistent weekly/monthly meetings with agendas and minutes, as well as a set format for the meeting notes. It has been proposed that the agenda for a meeting be made public as soon as possible, so that people can ensure their motions are included. A proposal for the format and rules of the meeting notes is included in the proposed constitution.
			\item A set of base rules for events, that can be accessed by all members (preferably both online and in print form).
			\item Removing the name "Lockwood Arms Group". The suggested new name is "Aber Live Action Gaming" or some variant thereof. Military vernacular should be avoided with regards to the society, as it's bad for public image. \\ - \by{Seth Khan, Sam Clements}
			\item Membership fees and benefits.
			\item Bilingualism.
		\end{itemize}

		\item \textbf{Health and Safety} \by{Tabby Key}
		\begin{itemize}
			\item Protocol for dealing with modified/unknown blasters. A list of all allowed weapons may be a good idea.
			\item Standardized risk assessment that can be modified for individual events.
			\item Proposal: No new weapons may be introduced during events, even if they would be labelled safe by Health and Safety Officer. Newly modded weapons allowed at Health and Safety officer's discretion. \by{Dave Haenze}
		\end{itemize}
 
		\item \textbf{Future events} \by{Dave Haenze}
		\begin{itemize}
			\item Freshers week.
			\item Next major event.
			\item Event/society graphics, as well as advertising.
			\item Contact Robert Grayston with running of Assassin.
		\end{itemize}
		
		\item \textbf{Online presence} \by{Dave Haenze}
		\begin{itemize}
			\item We have the domain aberlag.com - Samuel Clements is dealing with the new site, which is planned to include the kaos system written for RvB, and pages for society information, such as rules and the constitution.
			\item Committee members have been  provided with a name@aberlag.com email on request.
			\item Hosting is currently free and should not be an issue. However, the domain is ~£10 a year, which will need to come out of society funds. \by{Sam Clements}
		\end{itemize}
		
		\item \textbf{Problems} \by{Liam Williams}
		\begin{itemize}
			\item Noise complaints, residential areas.
			\item The recent election and problems with Keiran Russell.
		\end{itemize}
		
		\item Futher motions or points. \by{The committee}
		\item The date and time of the next general meeting. \by{The committee}
	\end{itemize}
\end{document}